West Africa cuckoo stopover rainfall patterns

### 2018-09-07 stopover_rainfall_ndvi_detailcoords_vis_DEPWAbirds.Rmd
small addition to make best plot

>>>>

#make epic plot
#ggplot(data=t2)+
#    geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, #ymax=500), fill='grey')+
#    geom_line( aes(x=variable, y=emodisNDVI*500), colour='light #green', size=1)+
#    geom_line(aes(x=variable, y=cumrf), col='blue', size=1)+
#    facet_wrap(~country, ncol=1)+theme_classic()+
#    ylab('Cumulative rainfall since 01 Jan (mm)')+ xlab('Day of #year')+
#  scale_y_continuous(limits=c(0,500),sec.axis = #sec_axis(~./500, name='NDVI'))
